---
runtime: shiny
output: html_document
---

```{r echo=FALSE}
library(babynames)
library(ggplot2)
```

## What's in a name?

Please select a name to explore.

```{r echo=FALSE}
textInput(inputId = "name", label = "Name:", value = "Gaston")
names <- reactive(subset(babynames, name == input$name))
```


Here is a graph of the number of people named `r renderText(input$name)`.

```{r echo=FALSE, fig.height=3, fig.width=5}
renderPlot(
  ggplot(data = names(), aes(x = year, y = n)) +
    geom_line(aes(color = sex), size = 1.5) + 
    theme_bw()
)
```

`r renderText(input$name)` was more popular than ever in 
`r renderText(names()$year[which.max(names()$n)])`. 
That year there were `r renderText(names()$n[which.max(names()$n)])` babies named `r renderText(input$name)`.
So far, `r renderText(sum(names()$n))` people have been named `r renderText(input$name)`. 

`r hr()`

Here's an example of `renderPrint()`
`r renderPrint(paste('Selected name is:', input$name))`

`r hr()`

Here's an example of `renderTable()` showing the last rows in the subset dataframe `babynames`:
`r renderTable(tail(names()))`

`r hr()`

Here's an example of `renderImage()`
```{r echo = FALSE}
renderImage({
  # A temp file to save the output.
  # This file will be removed later by renderImage
  outfile <- tempfile(fileext = '.png')
    
  # Generate the PNG
  png(outfile, width=400, height=300)
  plot(names()$year, names()$n, type = 'l',
       col = '#a2cd5a', lwd = 3,
       main="Generated in renderImage()")
  dev.off()
    
  # Return a list containing the filename
  list(src = outfile,
       contentType = 'image/png',
       width = 600,
       height = 500,
       pointsize = 20,
       alt = "This is alternate text")
  }, 
  deleteFile = TRUE
)
```


